The Concurrent Calculi Formalisation Benchmark

### 2023-10-11 paper/paper.tex
grammar
rephrasing in the going beyond section

As with the challenges that came before, this one is intended to be
useful on its own, but not to cover every problem that may be faced
when mechanising systems based on message passing calculi. The current
challenge can be extended in two dimensions: the first, about taking
the existing challenges further. And the second, about devising
challenges not covered by the current benchmarks.

@@

On the side of proof assistants, the current challenge proposes
mechanising the proofs of theorems. An interesting venue to explore
would be to take advantage of other aspects of proof assistants. For
example, proof assistants are often able to produce certified code (by
using code extraction, or compiling and running their definitions).
Additionally, while having effective automation in our current
challenge is possible, a challenge could be designed with the explicit
objective of automating aspects of the proofs. And finally, a
challenge could propose the integration with other formal reasoning
tools, namely model checkers. These tools are in common use in the
field. However, there combining automated proofs with proof assistants
could be a great path for attempting larger proofs with less effort.

>>>>

As with the challenges that came before, this one is intended to be
useful on its own, but not to exhaustively cover every possible
problem in the area. The current challenge can be extended in two
dimensions: the first is taking the existing challenges further.
And the second is devising new challenges not covered by the current
benchmarks.

@@

On the side of proof assistants, the current challenge proposes
mechanising the proofs of theorems. An interesting venue to explore
would be to take advantage of other aspects of proof assistants. For
example, proof assistants are often able to produce certified code (by
using code extraction, or compiling and running their definitions).
Additionally, while having effective automation in our current
challenge is possible, a challenge could be designed with the explicit
objective of automating aspects of the proofs. And finally, a
challenge could propose the integration with other formal reasoning
tools, namely model checkers. These tools are in common use in the
field. However, combining automated proofs with proof assistants
offers the potential to ease the path for attempting larger proofs
with less effort.
